---
title: "Text Analysis on Congressional Records"
author: "Shivani Sharma"
date: "2/9/2020"
output:
  html_document: default
  word_document: default
---
This data originally appeared in Gentzkow and Shapiro (GS; 2010) and considers text of the 2005 Congressional Record, containing all speeches in that year for members of the United States House and Senate. In particular, GS record the number times each of 529 legislators used terms in a list of 1000 phrases (i.e., each document is a year of transcripts for a single speaker). It also includes the ideology of each speaker –
Party: (Republican, Democrat, or Independent)
repshare: share of constituents voting for Bush in 2004

First Step: Fit K-means to the speech text of the members, comprising of the 1000 phrases, for K in 5,10,15,20,25
```{r}
library(textir)
library(maptpx)
load("congress.RData")
options(repos = c(CRAN = "http://cran.rstudio.com"))
fs <- scale(as.matrix( congress109Counts/rowSums(congress109Counts) ))


kfit <- lapply(seq(5,25,5), function(k) kmeans(fs,k))
```
Second Step: Use BIC to choose the K and interpret the selected model. Also use the elbow curve method to identify the most optimal value of K. Compare the two values of K that you obtained.

```{r}
kic <- function(fit, rule=c("A","B")){
	df <- length(fit$centers) # K*dim
	n <- sum(fit$size)
	D <- fit$tot.withinss # deviance
	rule=match.arg(rule)
	if(rule=="A")
		return(D + 2*df*n/(n-df-1))
	else
		return(D + log(n)*df)
}



KAICc_score <- sapply(kfit, kic, "A")
KAICc<-as.data.frame(KAICc_score)
KAICc$k<-seq(5,25,5)

View(KAICc)

plot(x=KAICc$k,y=KAICc$KAICc_score, xlab="K", ylab="AICc")
lines(KAICc$k,KAICc$KAICc_score, col=4, lwd=2)
abline(v=which.min(KAICc$kAICc_score),col=4)


deviance <- lapply(seq(5,25,5), function(k) kmeans(fs, k)$tot.withinss)
plot(seq(5,25,5), deviance, xlab="K", ylab="Deviance")
lines(seq(5,25,5), deviance, col=4)



install.packages("factoextra")
library(factoextra)
fviz_nbclust(fs, kmeans, method = "wss",k.max=25)


kfit <- lapply(seq(1,25,1), function(k) kmeans(fs,k))
KAICc_score <- sapply(kfit, kic, "A")
KAICc<-as.data.frame(KAICc_score)
KAICc$k<-seq(1,25,1)


plot(x=KAICc$k,y=KAICc$KAICc_score, xlab="K", ylab="AICc")
lines(KAICc$k,KAICc$KAICc_score, col=4, lwd=2)
abline(v=which.min(KAICc$kAICc_score),col=4)


kfit <- lapply(seq(1,25,1), function(k) kmeans(fs,k))


```


Third Step:Fit a topic model for the speech counts. Use Bayes factors to choose the number of topics and interpret your chosen model.
```{r}
#topic model
x <- as.simple_triplet_matrix(congress109Counts)

#bayes factor
tpcs <- topics(x, K=5*(1:5), verb=10)

summary(tpcs, n=10) 

install.packages("wordcloud")
library(wordcloud)

par(mfrow=c(1,2))
for (i in 1:10)
{
wordcloud(row.names(tpcs$theta), 
	freq=tpcs$theta[,i], min.freq=0.004, col="maroon")
}


```
Fourth Step: Connect the unsupervised clusters to partisanship. Tabulate party membership by K-means cluster. Are there any non-partisan topics? Fit topic regressions for each of party and repshare. Compare to regression onto phrase percentages: x <- 100 * congress109Counts / rowSums(congress109Counts)
```{r}
library(glmnet)


install.packages("dplyr")
library(dplyr)

#KMeans Cluster
#percentage of party wise candidates in each cluster
kfit <- lapply(seq(1,25,1), function(k) kmeans(fs,k))
k=20
party_cluster<-tapply(congress109Ideology$party, kfit[[k]]$cluster, table)

df<-data.frame()
x<-c("Democrats","Independent","Republicans")



#percentage of party wise candidates in each cluster
for( i in 1:20)
{
df[i,1]<- round(party_cluster[i][[1]][[1]]/(party_cluster[i][[1]][[1]]+party_cluster[i][[1]][[2]]+party_cluster[i][[1]][[3]]),3)
df[i,2]<- round(party_cluster[i][[1]][[2]]/(party_cluster[i][[1]][[1]]+party_cluster[i][[1]][[2]]+party_cluster[i][[1]][[3]]),3)
df[i,3]<-round(party_cluster[i][[1]][[3]]/(party_cluster[i][[1]][[1]]+party_cluster[i][[1]][[2]]+party_cluster[i][[1]][[3]]),3)

}

View(df)
colnames(df)<-x
View(df)

#Topics
#Partisanship of topics
all_topics_candidates<-as.data.frame(tpcs$omega)
colnames(all_topics_candidates)<-c("tp1","tp2","tp3","tp4","tp5","tp6","tp7","tp8","tp9","tp10")
all_topics_candidates$candidates<-rownames(all_topics_candidates)
congress109Ideology$candidates<-rownames(congress109Ideology)
party_topic_data<-merge(all_topics_candidates,congress109Ideology,by="candidates")

party_topic_sum<-party_topic_data%>% select(1,party,2,3,4,5,6,7,8,9,10,11) %>% group_by(party) %>% summarize(tp1_wt=sum(tp1),tp2_wt=sum(tp2),tp3_wt=sum(tp3),tp4_wt=sum(tp4),tp5_wt=sum(tp5),tp6_wt=sum(tp6),tp7_wt=sum(tp7),tp8_wt=sum(tp8),tp9_wt=sum(tp9),tp10_wt=sum(tp10))
party_topic_sum
d<-party_topic_sum %>% filter(party!="I")
d[,-1] = apply(d[,-1],2,function(x){round(x/sum(x),3)})
View(d)



```


```{r}
#regression
#party &repshare for republican on topics
rep_all <- party_topic_data %>% select(party,tp1,tp2,tp2,tp4,tp5,tp5,tp7,tp8,tp9,tp10,repshare)%>% filter(party=="R")
rep_omega<-as.matrix(rep_all%>% select(tp1,tp2,tp2,tp4,tp5,tp5,tp7,tp8,tp9,tp10))
rep_repshare<-rep_all$repshare
rep_regtopics.cv <- cv.glmnet(rep_omega, rep_repshare)



#party &repshare for democrats on topics
dem_all <- party_topic_data %>% select(party,tp1,tp2,tp2,tp4,tp5,tp5,tp7,tp8,tp9,tp10,repshare)%>% filter(party=="D")
dem_omega<-as.matrix(dem_all%>% select(tp1,tp2,tp2,tp4,tp5,tp5,tp7,tp8,tp9,tp10))
dem_repshare<-dem_all$repshare
dem_regtopics.cv <- cv.glmnet(dem_omega, dem_repshare)
```


```{r}

x <- 100 * congress109Counts / rowSums(congress109Counts) 
phrase<-as.data.frame(as.matrix(x))
phrases_col<-colnames(phrase)
phrase$candidates<-rownames(phrase)
congressparty<-congress109Ideology%>%select(name,party,repshare)
congressparty$candidates<-congressparty$name
party_phrase_data<-merge(phrase,congressparty,by="candidates")


#party &repshare for republican on phrase
rep_all <- party_phrase_data%>% filter(party=="R")
rep_phrase<-rep_all %>%select(-name,-party,-candidates,-repshare)
rep_phrase_mat<-as.matrix(rep_phrase)
rep_phrase_repshare<-rep_all$repshare
rep_regphrase.cv <- cv.glmnet(rep_phrase_mat, rep_phrase_repshare) 



#party &repshare for democrats on phrase
dem_all <- party_phrase_data%>% filter(party=="D")
dem_phrase<-dem_all %>%select(-name,-party,-candidates,-repshare)
dem_phrase_mat<-as.matrix(dem_phrase)
dem_phrase_repshare<-dem_all$repshare
dem_regphrase.cv <- cv.glmnet(dem_phrase_mat, dem_phrase_repshare)


# max OOS R^2s for republicans
max(1-rep_regtopics.cv$cvm/rep_regtopics.cv$cvm[1])
max(1-rep_regphrase.cv $cvm/rep_regphrase.cv $cvm[1])


# max OOS R^2s
max(1-dem_regtopics.cv$cvm/dem_regtopics.cv$cvm[1])
max(1-dem_regphrase.cv $cvm/dem_regphrase.cv $cvm[1])
```

Conclusions:
TOPICS	EMERGING THEMES
Topic 1	African-American Rights as the dominant words are Rosa Parks, Civil Rights, Luther King, Black Caucus
Topic 2	 Budget 
Topic 3	Immigration and Internal security
Topic 4	Foreign Policy and Defense
Topic 5	Economy and Employment
Topic 6	Environment: Climate Change & Energy Resources
Topic 7	Chief Justice & Judiciary
Topic 8	Gun industry and Laws & Poverty (Low income)
Topic 9	Trade & related Policy 
Topic 10	Embryonic stem

Partisanship in K-Means clusters:
We have taken K=20 and each of the clusters indicates a topic. There is clear dominance of the party observed for each topic(cluster) as the weightages of at least one of the parties is 0.7 or more. Hence, we do not observe any non-partisan topic through K-Means clustering.
Democrats	Independent	Republicans
			
1	0.160	0.000	0.840
2	0.778	0.000	0.222
3	0.714	0.143	0.143
4	1.000	0.000	0.000
5	0.000	0.000	1.000
6	0.692	0.000	0.308
7	0.000	0.000	1.000
8	1.000	0.000	0.000
9	0.800	0.000	0.200
10	1.000	0.000	0.000
11	0.100	0.000	0.900
12	0.000	0.000	1.000
13	1.000	0.000	0.000
14	0.000	0.000	1.000
15	0.000	0.000	1.000
16	0.240	0.000	0.760
17	1.000	0.000	0.000
18	0.309	0.004	0.687
19	0.000	0.000	1.000
20	0.171	0.000	0.829

Partisanship in Topic Clusters:

                 party	tp1_wt	tp2_wt	tp3_wt	tp4_wt	tp5_wt	tp6_wt	tp7_wt	tp8_wt	tp9_wt	tp10_wt
											
1	D	0.667	0.878	0.207	0.26	0.204	0.399	0.322	0.751	0.594	0.246
2	R	0.333	0.122	0.793	0.74	0.796	0.601	0.678	0.249	0.406	0.754

By observing the topic weightage percentage for the parties, we notice that topic_9 among all topics seems to non-partisan as the weightage % is in the similar range.

For republican parties:
•	on regressing topics on repshare we get R2  of ~0.0071
•	on regressing phrase percentage on repshare we get R2  of ~0.00081
For democrats:
•	on regressing topics on repshare we get R2  of ~0.123
•	on regressing phrase percentage on repshare we get R2  of ~0.116
Topic regression seems to better than phrase percentage regression in predicting the repshare especially for Democrats over Republicans.



